### 2018-09-07 gateVis-paper/intro.tex
update comments

>>>>

Outline
\begin{itemize}
    \item the important of LSTM/RNN
    \item the criptic natural of the hidden state, where a single state represents the whole sequence
    \item the need to understand how does the model remember and forget? especially in analysis long sequence in the real world scenarios
    \item Understand how the gate affect the prediction
\end{itemize}

Many recent advances of neural language processing is driven by the continoues evolving and improving of the recurrent neural networks. These model processes information in a sequenctial fashion, which can easily handle the flexible and variable length
